### 2022-12-21 index.qmd
start of initial site

---
title: "J. Derek Tucker"
subtitle: "Distinguished Member of Technical Staff, Sandia National Laboratories\\ Adjunct Professor, Department of Statistics, University of Illinois"
image: images/me.jpg
about:
  template: trestles
  links:
    - icon: linkedin
      url: "https://linkedin.com/in/derek-tucker-04247818"
    - icon: github
      url: "https://github.com/jdtuck"
    - icon: google
      url: "https://scholar.google.com/citations?user=1jdvTZwAAAAJ&hl=en"
    - icon: file-pdf
      url: "http://arxiv.org/a/tucker_j_1"
    - icon: bi-envelope
      url: "mailto:jdtuck@sandia.gov"
    - text: CV
      href: "Docs/JDT_CV.pdf"
resources:
    - "Docs/JDT_CV.pdf"
---
::: {.column-page}

## Bio
I obtained my Ph.D. in Statistics from [Florida State University](http://www.fsu.edu/). I received the B.S. and M.S. degrees from [Colorado State University](https://www.colostate.edu/), Fort Collins, in 2007 and 2009, respectively, both in electrical engineering, with an emphasis on statistical signal processing. My dissertation was advised by [Anuj Srivastava](http://ani.stat.fsu.edu/~anuj/) and [Wei Wu](http://ani.stat.fsu.edu/~wwu/) and focused modeling of unaligned functional data. Currently, I am a Distinguished Member of the Technical Staff at Sandia National Laboratories in Albuquerque, NM and an adjunct faculty member of the Department of Statistics at the University of Illinois. At Illinois I teach a topics course on functional data analysis. Recently, I received the Director of National Intelligence Team Award for contributions to the Signal Location in Complex Environments (SLiCE) team.

My main interest lies in the area of functional data analysis with a focus on geometric methods and unaligned data. I recently have emphasized on statistical analysis and modeling of this type of data. My other research interests include statistical image understanding, statistical learning methods, and point processes.

## Education

My full CV is available [here](Docs/JDT_CV.pdf).

**Florida State University**
Tallahasee, FL

Ph.D. in Statistics | August 2011 - June 2014

**Colorado State University**
Fort Collins, CO

M.S. in Electrical Engineering | August 2007 - May 2009\
B.S. in Electrical Engineering | August 2004 - May 2007

## Contact Information

J. Derek Tucker			
[Statistical Sciences](http://www.sandia.gov/statistics/)  
[Sandia National Laboratories](http://www.sandia.gov/)  
PO Box 5800 MS 0829		
Albuquerque, NM 87185

Email SNL: [jdtuck@sandia.gov](mailto:jdtuck@sandia.gov)  
Email UIUC: [dtucker1@illinois.edu](mailto:dtucker1@illinois.edu)  
Phone: 505-284-8415

:::

### 2022-12-21 papers.qmd
start of initial site

---
title: "Papers"
---

<br>
<font size="5">[Google Scholar Page](https://scholar.google.com/citations?user=1jdvTZwAAAAJ&hl=en)</font> 
<br>

COPYRIGHT NOTICE: The material listed here are copyrighted. Personal use of this material is permitted. However, permission to reprint/publish this material for advertising or promotional purposes or for creating new collective works for resale or redistribution to servers or lists, or to reuse any copyrighted component of this work in other works must be obtained from the copyright holder.

## 2022
**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection", *Envirometrics*, submitted, 2022. [arxiv preprint](https://arxiv.org/abs/2211.12687)

J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics *, submitted, 2022.

K. Rumsey, and J. G. Huerta, and **J. D. Tucker**, "A Localized Ensemble of Approximate Gaussian Processes for Fast Sequential Emulation", *Stat*, submitted, 2022.

**J. D. Tucker**, M. T. Martinez, and J. M. Laborde, "Dimensionality Reduction using Elastic Measures", *Stat*, submitted, 2022. [arxiv preprint](https://arxiv.org/abs/2209.04933)

M. A. Ausdemore, A. McCombs, D. Ries, A. Zhang, K. Shuler, K. Goode, **J. D. Tucker** and J. G. Huerta, “A Probabilistic Inverse Prediction Method for Predicting Plutonium Processing Conditions”, *Frontiers in Nuclear Engineering-Nuclear Materials*. accepted 2022.[PDF](Papers/PuBASS_Frontiers_2022.pdf)

D. Ries, A. Zhang, **J. D. Tucker**, K. Shuler, and  M. Ausdemore, "A framework for inverse prediction using functional response data", *JCISE*, 10.1115/1.4053752, 2022 [PDF](Papers/JCISE-21-1393.pdf)

## 2021
L. Patel, L. Shand, **J. D. Tucker**, and  G. Huerta, "Spatio-temporal extreme event modeling of terror insurgencies", *arXiv:2110.08363 [stat.AP]*, 2021 [arxiv](https://arxiv.org/abs/2110.08363)

T. Harris, B. Li, and **J. D. Tucker**. "Scalable Multiple Changepoint Detection for Functional Data Sequences", *Environmetrics*, 10.1002/env.2710, 2021. [PDF](Papers/Harris_Environmetrics_21.pdf)

C. Ting, N. Johson, U. Onunkwo, and **J. D. Tucker**. "Faster classification using compression analytics", *IEEE ICDM Workshop on Data Mining and Machine Learning for Cybersecurity*, 2021. [PDF](Papers/IEEEDML_CYber21.pdf)

**J. D. Tucker**, L. Shand, and K. Chowdhary. "Multimodal Bayesian Registration of Noisy Functions using Hamiltonian Monte Carlo", *Computational Statistics and Data Analysis*, 10.1016/j.csda.2021.107298, 2021. [PDF](Papers/CSDA_Bayesian_21.pdf)

## 2020
X. Zhang, S. Kurtek, O. Chkrebtii, and **J. D. Tucker**, "Elastic $k$-means clustering of functional data for posterior exploration, with an application to inference on acute respiratory infection dynamics", *arXiv:2011.12397 [stat.ME]*, 2020 [arxiv](http://arxiv.org/abs/2011.12397)

A. H. Foss, R. B. Lehoucq, W. Z. Stuart, **J. D. Tucker**, and J. W. Berry, "A Deterministic Hitting-Time Moment Approach to Seed-set Expansion over a Graph", *arXiv:2011.09544 [cs.SI]*, 2020. [arxiv](http://arxiv.org/abs/2011.09544)

L. Patel, L. Shand, **J. D. Tucker**, and G. Huerta, "Assessing Extreme Value Analysis to predict rare events from the Global Terrorism Database,'' *Proc JSM*, August 2020 [PDF](Papers/JSM20.pdf)

T. Harris, B. Li, N. J. Steiger, J. E. Smerdon, N. Narisetty, and **J. D. Tucker**. "Testing the exchangeability of two ensembles of spatial processes - Evaluating proxy influence in assimilated paleoclimate reconstructions"  *Journal of the American Statistical Association*, 10.1080/01621459.2020.1799810, 2020. [[PDF](Papers/JASA20_proxy.pdf)
| [R](Code/JASA20_proxy_supp.zip)]

C. King, N. Martin, and **J. D. Tucker**. "Bounding Uncertainty in Functional Data: A Case Study in Reliability" *Quality Engineering*, vol. 33, no. 1, 2021. [PDF](Papers/King_QE_20.pdf)

T. Harris, **J. D. Tucker**, B. Li, and L. Shand, "Elastic depths for detecting shape anomalies in functional data," *Technometrics*, 10.1080/00401706.2020.1811156, 2020. [[PDF](Papers/Technometrics20_edepth.pdf)
| [R](Code/Technometrics20_edepth_supp.zip)]

M. K. Ahn, **J. D. Tucker**, W. Wu, and A. Srivastava. "Regression Models Using Shapes of Functions as Predictors" *Computational Statistics and Data Analysis*, 10.1016/j.csda.2020.107017, 2020. [PDF](Papers/Ahn_CSDA_20.pdf)

S. Reza, N. Martin, T. Buchheit, and **J. D. Tucker**, "Tolerance Bound Calculation for Compact Model Calibration Using Functional Data Analysis," Proc ETDM20, 2020.

## 2019
**J. D. Tucker**, J. R. Lewis, C. King, and S. Kurtek, "A Geometric Approach for Computing Tolerance Bounds for Elastic Functional Data," *Journal of Applied Statistics*, vol. 47, no 3. pp. 481-505, 2019. [PDF](Papers/JAS20_TB.pdf)

Y. Guan, C. Sampson, **J. D. Tucker**, W. Chang, A. Mondal, M. Haran, and D. Sulsky, "Computer model calibration based on image warping metrics: an application for sea ice deformation," *Journal of Agricultural, Biological and Environmental Statistics*, vol 41, pp 444–463, 2019 [PDF](Papers/Guan2019_Article_ComputerModelCalibrationBasedO.pdf)

## 2018
**J. D. Tucker**, L. Shand, and J. R. Lewis, "Handling Missing Data in Self-Exciting Point Process Models," *Spatial Statistics*, vol. 29. pp. 160-176, 2019. [PDF](Papers/SPATSTAT18_STPP.pdf)

**J. D. Tucker**, J. R. Lewis, and A. Srivastava, "Elastic Functional Principal Component Regression," *Statistical Analysis and Data Mining*, vol. 12, no. 2, pp. 101-115, 2019. [PDF](Papers/SADM18_elastic_regression.pdf)

T. Harris, B. Li, N. Steiger, J. Smerdon, and **J. D. Tucker**. "Evaluating Proxy Influence in Data Assimilation," *Proc Climate Informatics*, September 2018

T. Harris, B. Li, N. Steiger, J. Smerdon, and **J. D. Tucker**. "Evaluating proxy influence in data assimilation based climate field reconstruction,." *Proc JSM*, August 2018

M. K. Ahn, **J. D. Tucker**, W. Wu, and A. Srivastava. "Elastic handling of predictor phase in functional regression models." *International Workshop on DIFF-CVML: Differential Geometry in Computer Vision and Machine Learning, IEEE Conference on Computer Vision and Pattern Recognition (CVPR) Workshop*, June 2018. [PDF](Papers/CVPR18.pdf)

## 2017
J. Ramirez, M. Orini, **J. D. Tucker**, P. Laguna, and E. Pueyo, "Variability of Ventricular Repolarization Dispersion Quantified by Time-Warping the Morphology of the T-waves," *IEEE Transactions on Biomedical Engineering*, vol. 64, no. 7, pp. 1619-1630, 2017. [PDF](Papers/TBME_Ramirez.pdf)

## 2016
D. Bryner, F. Huffer, M. M. Rosenthal, **J. D. Tucker**, and A. Srivastava, "Linear Minelayer Trajectory Estimation Using Cluttered Point Cloud Data," *Computational Statistics and Data Analysis*, vol. 102, pp. 1-22, October 2016 [PDF](Papers/darshan_csda_2016.pdf)

J. Ramirez, M. Orini, **J. D. Tucker**, P. Laguna, and E. Pueyo, "An Index for T‐wave Pointwise Amplitude Variability Quantification,'' *Proc CinC (Mortara Winner)*, September 2016. [PDF](Papers/CINC16.pdf)

**J. D. Tucker**, "Functional Statistical Process Control using Elastic Methods,'' *Proc JSM*, August 2016. [PDF](Papers/JSM16.pdf)

D. Bryner, F. Huffer, A. Srivastava, and **J. D. Tucker**, "Underwater Mine Detection In Clutter Data Using Spatial Point Process Models," *IEEE Journal of Oceanic Engineering*, vol 41, no. 3. pp 670-681, 2016 [PDF](Papers/JOE-07398189.pdf)

T. G-Michael, B. Marchand, **J. D. Tucker**, D. D. Sternlicht, T. M. Marston, and M. R. Azimi-Sadjadi, "Image-based Automated Change Detection for Synthetic Aperture Sonar," *IEEE Journal of Oceanic Engineering*, vol 41, no. 3. pp 592-612, 2016. [PDF](Papers/JOE-07323881.pdf)

T. G-Michael, **J. D. Tucker**, and R. R. Roberts, "Statistically Normalized Coherent Change Detection for Synthetic Aperture Sonar Imagery," *Proc SPIE*, April 2016. [PDF](Papers/SPIE16.pdf)

## 2014
**J. D. Tucker**, W. Wu, and A. Srivastava, "Phase-Amplitude Separation of Proteomics Data Using Extended Fisher-Rao Metric," *Electronic Journal of Statistics*, vol 8, no. 2. pp 1724-1733, 2014. [[PDF](Papers/euclid.ejs.1414588155.pdf) | [Code](https://cran.r-project.org/web/packages/fdasrvf/index.html)]

T. G-Michael, B. Marchand, **J. D. Tucker**, D. D. Sternlicht, and T. M. Marston,"Automated Change Detection for Synthetic Aperture Sonar," *Proc SPIE*, May 2014. [PDF](Papers/spie14.pdf)

**J. D. Tucker**, W. Wu, and A. Srivastava, "Analysis of signals under compositional noise with applications to SONAR data," *IEEE Journal of Oceanic Engineering*, vol 29, no. 2. pp 318-330, Apr 2014. [[PDF](Papers/IEEEJOE_AC.pdf) | [Code](https://cran.r-project.org/web/packages/fdasrvf/index.html)]

## 2013
**J. D. Tucker**, W. Wu, and A. Srivastava, "Generative Models for Function Data using Phase and Amplitude Separation," *Computational Statistics and Data Analysis*, vol. 61, pp. 50-66, May 2013. [[PDF](Papers/CSDA_PCA_12.pdf)
| [R](https://cran.r-project.org/web/packages/fdasrvf/index.html)
| [MATLAB](https://github.com/jdtuck/fdasrvf_MATLAB)
| [Python](https://github.com/jdtuck/fdasrsf_python)
| [Julia](https://github.com/jdtuck/ElasticFDA.jl)]

## 2012
**J. D. Tucker**, W. Wu, and A. Srivastava, "Analysis of Signals Under Compositional Noise with Application to SONAR Data," *Proc. of MTS/IEEE Oceans 2012 Conference*, pp. 1-6, Oct. 2012. [PDF](Papers/Oceans12.pdf)

## 2011
**J. D. Tucker** and N. Klausner, "Compressive Sensing for Gauss-Gauss Detection,'' *Proc. of IEEE SMC 2011 Conference*, pp. 3335-3340, Oct. 2011. [PDF](Papers/SMC11.pdf)

J. C. Isaacs and **J. D. Tucker**, "Diffusion features for target specific recognition with synthetic aperture sonar raw signals and acoustic color," *Computer Vision and Pattern Recognition Workshops (CVPRW), 2011 IEEE Computer Society Conference on*, pp.27-32, 20-25 June 2011. [PDF](Papers/CVPR11.pdf)

**J. D. Tucker** and A. Srivastava,"Statistical analysis and classification of acoustic color functions,'' *Proc SPIE*, vol. 8017, pp. O1-O10, April 2011. [PDF](Papers/SPIE11.pdf)

**J. D. Tucker** and M. R. Azimi-Sadjadi, "Coherence-based underwater target detection from multiple sonar platforms," *IEEE Journal of Oceanic Engineering*, vol. 36, no. 1, pp. 37-51, Jan. 2011. [PDF](Papers/JOE11.pdf)

J. C. Isaacs and **J. D. Tucker**, "Signal diffusion features for automatic target recognition in synthetic aperture sonar," *Proc of IEEE DSP/SPE 2011 Workshop*, pp.461-465, Jan. 2011. [PDF](Papers/DSPE11-2.pdf)

**J. D. Tucker**, J. T. Cobb, and M. R. Azimi-Sadjadi, "Generalized likelihood ratio test for finite mixture model of K-distributed random variables" *Proc of IEEE DSP/SPE 2011 Workshop*, pp. 443-448, Jan. 2011. [PDF](Papers/DSPE11.pdf)

## 2010
T. G-Michael and **J. D. Tucker**, "Canonical correlation analysis for coherent change detection in synthetic aperture sonar imagery," *Proc of IEEE SAR/SAS 2010 Conference*, vol. 32, no. 4, pp. 117-122, Sep. 2010. [PDF](Papers/CCA_SAS-CCD.pdf)

N. Klausner, M. R. Azimi-Sadjadi, and **J. D. Tucker**, "Multi-sonar target detection using multi-channel coherence analysis," *Proc. of MTS/IEEE Oceans 2010 Conference*, pp. 1-7, Sept. 2010. [PDF](Papers/Oecans10.pdf)

**J. D. Tucker** and M. R. Azimi-Sadjadi,"Neyman pearson detection of K-distributed random variables," *Proc SPIE*, vol. 7664, pp. Q1-Q12, April 2010. [PDF](Papers/SPIE10.pdf)

## 2009
M. Kabatek, M. R. Azimi-Sadjadi, and **J. D. Tucker**, "An underwater target detection system for electro-optical imagery data,'' *Proc. of MTS/IEEE Oceans 2009 Conference*, pp. 1–8, October 2009. [PDF](Papers/Oceans09-EO.pdf)

N. Klausner, **J. D. Tucker**, and M. R. Azimi-Sadjadi, "Multi-platform target detection using multi-channel coherence analysis and robustness to the effects of disparity,'' *Proc. of MTS/IEEE Oceans 2009 Conference*, pp. 1–7, October 2009. [PDF](Papers/Oceans09.pdf)

N. Klausner, M. R. Azimi-Sadjadi, and **J. D. Tucker**, "Underwater target detection from multi-platform sonar imagery using multi-channel coherence analysis,'' *Proc. of IEEE SMC 2009 Conference*, pp. 2728–2733, 2009. [PDF](Papers/SMC09.pdf)

## 2008
**J. D. Tucker** and M. R. Azimi-Sadjadi, "Coherence-based underwater target detection and classification for side-scan sonar imagery," *Sea Technology Magazine*, vol. 12, pp. 10-14, December 2008. [PDF](Papers/seatechnology08.pdf)

**J. D. Tucker**, N. Klausner, M. R. Azimi-Sadjadi, "Target detection in m-disparate sonar platforms using multichannel Hypothesis Testing," *Proc. IEEE/MTS Oceans 2008*, pp. 1-7, September 2008. [PDF](Papers/oceans08.pdf)

**J. D. Tucker**, M. R. Azimi-Sadjadi, "Target detection from dual disparate sonar platforms using canonical correlations," *Proc. SPIE*, vol. 6553, pp. 65530U– 1–65520U–8, March 2008. [PDF](Papers/spie08.pdf)

## 2007
**J. D. Tucker**, M. R. Azimi-Sadjadi, and G. J. Dobeck, "Canonical coordinates for detection and classification of underwater objects from sonar imagery," *Proceedings of IEEE Oceans 2007*, pp. 1-6, June 2007. [PDF](Papers/oceans07.pdf)

**J. D. Tucker**, M. R. Azimi-Sadjadi, and G. J. Dobeck, "Coherent-based method for detection of underwater objects from sonar imagery," *Proc. SPIE*, vol. 6553, pp. 65530U– 1–65520U–8, April 2007. [PDF](Papers/spie07.pdf)

## Invited Talks
"Elastic Functional Data Analysis", *SMU Statistical Colloquium*, November 4, 2022

"Elastic Functional Tolerance Bounds", *LANL Statistical Colloquium*, December 16, 2020

"Elastic Functional Data Analysis", *Brigham Young University Statistics Colloquium*, December 4, 2019

"Sandia Applications of Functional Data Analysis", *University of Illinois Statistics Colloquium*, November 22, 2019

"Elastic Functional Data Analysis", *Australian National University Statistics Colloquium*, July 12, 2018

"Elastic Functional Data Analysis", *University of New Mexico Statistics Colloquium*, February 2, 2018

"Doppler Multi-INT Detection and Tracking", *NSWC-PCD Invited Lecture*, October 1, 2015

"Alignment and Analysis of Proteomics Data using Square Root Slope Function Framework'', *CTW: Statistics of Time Warpings and Phase Variations 2012*, OSU MBI, Nov 7, 2012 [PDF](Presentations/MBI2012_Tucker.pdf)

"Statistical Analysis and Modeling of Elastic Functions'', *Department of Mathematical and Statistical Sciences, University of Alberta*, Aug 23, 2011. (Organizer: Yau Shu Wong) [PDF](Presentations/UA-Function_Warping.pdf)

## Patents
"Method and system for training an artifical neural network utilizing physics based knowledge" US Patent No. Applied

"Automated Change Detection Technique for Synthetic Aperture Sonar" US Patent No. US10049295B2 [PDF](Papers/US10049295.pdf)

### 2022-12-21 research.qmd
start of initial site

---
title: "Research"
---

My main interest lies in the area of statistical signal and image understanding with a focus on theoretical issues. This research area has also been called computational vision since one seeks to design computerized systems for understanding scenes from camera images, much like our own human vision system. There is a strong need for such tools in **medical diagnostics, face recognition, video surveillance, undersea imaging, terrain mapping**, and **satellite image analysis**. In military domain, the problem of battlefield target recognition continues to motivate newer research which is a vast importance

My current focus is in the area of functional data analysis the focus on the registration and statistical analysis functions in $\mathbb{R}^n$ and images. Specifically, looking at uncertainty quantification and regression modeling of this type of data. Small changes in the sensor placement introduce compositional noise in this type of data. The traditional alignment techniques are based on energy functions that are not proper distances, and necessitate a separate (and thus suboptimal) choice of distance to compare the aligned functions. I work on methods that present a comprehensive technique, for removing compositional noise and aligning functions, that: (1) uses a single cost function for data alignment, (2) combines the data and smoothness in natural fashion, and (3) leads to a proper distance between aligned functions. It is based on establishing re-parameterization orbits of functions under the warping group and defining a distance between orbits using the Fisher-Rao metric. Using this metric we can compute a proper covariance and perform functional principal component analysis. From the principal components we can develop models of the y variability (aligned data) and x variability (warping functions) and perform classification. I have investigated the use of this framework in modeling and classification of spectral signatures in acoustic data, image registration and classification, and tolerance bound generation.

<center><img src="images/ResearchFigure.jpg" alt="kinematics" style="width:80%; border:0px solid"></center>

[Sandia Statistical Sciences](http://www.sandia.gov/statistics/)	
[FSU Statistical Shape and Modeling Group](http://ssamg.stat.fsu.edu/)

[FDA Datasets](https://github.com/jdtuck/fda_datasets)

### 2022-12-21 resume.qmd
start of initial site

---
title: "Resume"
---

[Detailed CV](Docs/JDT_CV.pdf)

### Research Interests
Statistical Image Understanding, Signal Analysis, Target Classification, Detection Theory, Computational Statistics

### Education
**Doctor of Philosophy** in Statistics (2014)		
*Florida State University, Tallahassee, FL*		
**Thesis title:** Functional Component Analysis and Regression Using Elastic Methods [PDF](Papers/dissertation.pdf)		
**Thesis advisor:** Prof. Anuj Srivastava		
**Thesis co-advisor:** Prof. Wei Wu

**Master of Science** in Electrical Engineering (2009)		
*Colorado State University, Fort Collins, CO*		
**Thesis title:** Coherence-based Underwater Target Detection for Side-Scan Sonar Imagery [PDF](Papers/MS%20Thesis.pdf)		
**Thesis advisor:** Prof. Mahmood Azimi

**Bachelor of Science** in Electrical Engineering (2007)		
*Colorado State University, Fort Collins, CO*		
**Senior project:** Magnetic Spin Wave Detection and Localization

### Experience	
**Adjunct Faculty** (2020-Present)
University of Illinois
Department of Statistics
Champaign, IL

**Distinguished Member of Technical Staff** (2022-Present)				
Sandia National Laboratories		
Statistical Sciences		
Albuquerque, NM

**Principal Member of Technical Staff** (2017-2022)				
Sandia National Laboratories		
Statistical Sciences		
Albuquerque, NM

**Senior Member of Technical Staff** (2014-2017)				
Sandia National Laboratories		
Statistical Sciences		
Albuquerque, NM

**Research Assistant** (2011-2014)		
Statistics		
Florida State University, Tallahassee, FL

**Research Engineer** (2009 - 2014)		
Naval Surface Warfare Center		
Panama City Division - Code X13		
Panama City, FL

**Research Engineer** (2007 - 2009)		
Information System Technologies, INC 		
Fort Collins, CO

**Research Assistant** (2006-2009)		
Digital Signal and Image Laboratory		
Colorado State University, Fort Collins, CO

### Affiliations	
IEEE (Senior Member), ASA, SIAM

### 2022-12-21 software.qmd
start of initial site

---
title: "Software"
---

## `fdasrvf`
I'm lead author of the `fdasrvf` R package ([CRAN](https://cran.r-project.org/web/packages/fdasrvf/index.html); [GitHub](https://github.com/jdtuck/fdasrvf_R)).

This package performs alignment, PCA, and modeling of multidimensional and unidimensional functions using the square-root velocity framework (Srivastava et al., 2011 [arXiv:1103.3817](https://arxiv.org/abs/1103.3817) and Tucker et al., 2013 [doi:10.1016/j.csda.2012.12.001](Papers/CSDA_PCA_12.pdf)). This framework allows for elastic analysis of functional data through phase and amplitude separation. Multiple papers utilize the work in this package and is listed in the [CRAN Functional Data Analysis Task View](https://cran.r-project.org/web/views/FunctionalData.html). See the package README for all the methods it implements and reference papers.

There are also version of this code for [MATLAB](https://github.com/jdtuck/fdasrvf_MATLAB), and [Julia](https://github.com/jdtuck/ElasticFDA.jl)

Documentation for the Julia (Documentation: [HTML](http://elasticfdajl.readthedocs.org/en/latest/))

## `fdasrsf`
I'm lead author of the `fdasrsf` python package ([PYPI](https://cran.r-project.org/web/packages/fdasrvf/index.html);
[Conda](https://anaconda.org/conda-forge/fdasrsf);
[GitHub](https://github.com/jdtuck/fdasrsf_python)).

This package performs alignment, PCA, and modeling of multidimensional and unidimensional functions using the square-root velocity framework (Srivastava et al., 2011 [arXiv:1103.3817](https://arxiv.org/abs/1103.3817) and Tucker et al., 2013 [doi:10.1016/j.csda.2012.12.001](Papers/CSDA_PCA_12.pdf)). This framework allows for elastic analysis of functional data through phase and amplitude separation. Multiple papers utilize the work in this work and listed in the documentation. See the package README for all the methods it implements and reference papers.

Documentation for the Python (Documentation: [HTML](https://fdasrsf-python.readthedocs.io/en/latest/?badge=latest))

### 2022-12-21 index.qmd
update description

@@
 title: "J. Derek Tucker"
-subtitle: "Distinguished Member of Technical Staff, Sandia National Laboratories\\ Adjunct Professor, Department of Statistics, University of Illinois"
+description: | 
+             | *Distinguished Member of Technical Staff*, Sandia National Laboratories 
+             | *Adjunct Professor*, Department of Statistics, University of Illinois
 image: images/me.jpg
@@
 ---
+
 ::: {.column-page}

### 2023-01-18 papers.qmd
update slides

@@
 ## Invited Talks
-"Elastic Functional Data Analysis", *SMU Statistical Colloquium*, November 4, 2022
+"Elasic Bayesian Model Calibration" *FSU Shape Group Statistical Meeting*, January 24, 2023, [Slides](https://jdtuck.github.io/presentations/FSU_Jan23/FSU_Jan23.html)
+
+"Elastic Functional Data Analysis", *SMU Statistical Colloquium*, November 4, 2022, [Slides](Presentations/2022SMU_Nov_22.pdf)
 
@@
 
-"Alignment and Analysis of Proteomics Data using Square Root Slope Function Framework'', *CTW: Statistics of Time Warpings and Phase Variations 2012*, OSU MBI, Nov 7, 2012 [PDF](Presentations/MBI2012_Tucker.pdf)
+"Alignment and Analysis of Proteomics Data using Square Root Slope Function Framework'', *CTW: Statistics of Time Warpings and Phase Variations 2012*, OSU MBI, Nov 7, 2012 [Slides](Presentations/MBI2012_Tucker.pdf)
 
 "Statistical Analysis and Modeling of Elastic Functions'', *Department of Mathematical and Statistical Sciences, University of Alberta*, Aug 23, 2011.
-(Organizer: Yau Shu Wong) [PDF](Presentations/UA-Function_Warping.pdf)
+(Organizer: Yau Shu Wong) [Slides](Presentations/UA-Function_Warping.pdf)
 

### 2023-02-13 papers.qmd
fix link
update papers

@@
 
-## 2022
+## 2023
 **J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection", *Envirometrics*, submitted, 2022. [arxiv preprint](https://arxiv.org/abs/2211.12687)
-
-J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics *, submitted, 2022.
 
@@
 
+J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics *, accepted, 2022.
+
+## 2022
 M.
@@
 Huerta, “A Probabilistic Inverse Prediction Method for Predicting Plutonium Processing Conditions”, *Frontiers in Nuclear Engineering-Nuclear Materials*.
-accepted 2022.[PDF](Papers/PuBASS_Frontiers_2022.pdf)
+10.3389/fnuen.2022.1083164, 2022.[PDF](Papers/PuBASS_Frontiers_2022.pdf)
 
@@
 
-"Elastic Functional Data Analysis", *SMU Statistical Colloquium*, November 4, 2022, [Slides](Presentations/2022SMU_Nov_22.pdf)
+"Elastic Functional Data Analysis", *SMU Statistical Colloquium*, November 4, 2022, [Slides](Presentations/SMU_Nov_22.pdf)
 

### 2023-03-17 papers.qmd
update accepted papers
update papers

@@
 
-**J. D. Tucker**, M. T. Martinez, and J. M. Laborde, "Dimensionality Reduction using Elastic Measures", *Stat*, submitted, 2022. [arxiv preprint](https://arxiv.org/abs/2209.04933)
+**J. D. Tucker**, M. T. Martinez, and J. M. Laborde, "Dimensionality Reduction using Elastic Measures", *Stat*, accepted, 2022. [arxiv preprint](https://arxiv.org/abs/2209.04933)
 
-J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics *, accepted, 2022.
+J.
+Upston, D.
+Sulsky, **J.
+D.
+Tucker**, and Y.
+Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics *, /10.1016/j.cam.2023.115126, 2022.
+[PDF](Papers/1-s2.0-S0377042723000705-main.pdfupda)
 

### 2023-03-17 papers.qmd
fix doi

@@
 Tucker**, and Y.
-Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics *, /10.1016/j.cam.2023.115126, 2022.
+Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics*, 10.1016/j.cam.2023.115126, 2022.
 [PDF](Papers/1-s2.0-S0377042723000705-main.pdfupda)

### 2023-03-29 papers.qmd
update papers

@@
 
-**J. D. Tucker**, M. T. Martinez, and J. M. Laborde, "Dimensionality Reduction using Elastic Measures", *Stat*, accepted, 2022. [arxiv preprint](https://arxiv.org/abs/2209.04933)
+**J. D. Tucker**, M. T. Martinez, and J. M. Laborde, "Dimensionality Reduction using Elastic Measures", *Stat*, 10.1002/sta4.551, 2023. [arxiv preprint](https://arxiv.org/abs/2209.04933)
 
@@
 Tucker**, and Y.
-Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics*, 10.1016/j.cam.2023.115126, 2022.
+Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics*, 10.1016/j.cam.2023.115126, 2023.
 [PDF](Papers/1-s2.0-S0377042723000705-main.pdfupda)

### 2023-05-01 papers.qmd
update pdf
update
update papers

@@
 
-K. Rumsey, and J. G. Huerta, and **J. D. Tucker**, "A Localized Ensemble of Approximate Gaussian Processes for Fast Sequential Emulation", *Stat*, submitted, 2022.
+K. Rumsey, and J. G. Huerta, and **J. D. Tucker**, "A Localized Ensemble of Approximate Gaussian Processes for Fast Sequential Emulation", *Stat*, 10.1002/sta4.576, 2023. [PDF](Papers/leapGP23.pdf)
 
-**J. D. Tucker**, M. T. Martinez, and J. M. Laborde, "Dimensionality Reduction using Elastic Measures", *Stat*, 10.1002/sta4.551, 2023. [arxiv preprint](https://arxiv.org/abs/2209.04933)
+**J. D. Tucker**, M. T. Martinez, and J. M. Laborde, "Dimensionality Reduction using Elastic Measures", *Stat*, 10.1002/sta4.551, 2023. [PDF](Papers/Stat23.pdf)
 
@@
 Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics*, 10.1016/j.cam.2023.115126, 2023.
-[PDF](Papers/1-s2.0-S0377042723000705-main.pdfupda)
+[PDF](Papers/1-s2.0-S0377042723000705-main.pdf)
 

### 2023-06-28 papers.qmd
add paper
add SPIE paper

@@
 ## 2023
+Christian A.
+Pattyn, Alexander W.
+Edstrom, Andres L.
+Sanchez, Karl Westlake, John D.
+van der Laan, **J.
+Derek Tucker**, Jessica Jones, Kaylin Hagopian, Joshua C.
+Shank, Lilian K.
+Casias, Jeremy B.
+Wright, "Event-based sensing for the detection of modulated signals in degraded visual environments", *Proc.
+SPIE 12514, Image Sensing Technologies: Materials, Devices, Systems, and Applications X, 1251409*, 2023.
+[PDF](Papers/SPIE23.pdf)
+
+D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)
+
 **J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection", *Envirometrics*, submitted, 2022. [arxiv preprint](https://arxiv.org/abs/2211.12687)

### 2023-08-09 software.qmd
add stpphawkes R package

@@
 Documentation for the Python (Documentation: [HTML](https://fdasrsf-python.readthedocs.io/en/latest/?badge=latest))
+
+## `stpphawkes`
+I'm the lead author of the `stpphawkes` R package ([GitHub](https://github.com/sandialabs/stpphawkes)).
+
+A R package for modeling of spatio-temporal and temporal point process using a Hawkes model accounting for missing data from the paper J.
+D.
+Tucker, L.
+Shand, and J.
+R.
+Lewis, "Handling Missing Data in Self-Exciting Point Process Models," Spatial Statistics, vol.
+29.
+pp.
+160-176, 2019.
+[PDF](Papers/SPATSTAT18_STPP.pdf)

### 2023-08-10 papers.qmd
update title
add paper

@@
 ## 2023
+D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint]()
+
 Christian A.
@@
 
-**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection", *Envirometrics*, submitted, 2022. [arxiv preprint](https://arxiv.org/abs/2211.12687)
+**J.
+D.
+Tucker** and D.
+Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, in revision, 2023.
+[arxiv preprint](https://arxiv.org/abs/2211.12687)
 

### 2023-08-16 software.qmd
update link

@@
 ## `stpphawkes`
-I'm the lead author of the `stpphawkes` R package ([GitHub](https://github.com/sandialabs/stpphawkes)).
+I'm the lead author of the `stpphawkes` R package ([CRAN](https://cran.r-project.org/web/packages/stpphawkes/index.html);[GitHub](https://github.com/sandialabs/stpphawkes)).
 

### 2023-10-09 papers.qmd
add link
add JAP paper
format fix
updates to acceptance

@@
 ## 2023
-D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint]()
+J.
+Brown, J.
+P.
+Davis, **J.
+D.
+Tucker**, J.
+G.
+Huerta, and K.
+Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, submitted 2023.
+
+D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2308.05915)
+
+D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)
 
@@
 
-D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)
-
 **J.
@@
 Tucker** and D.
-Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, in revision, 2023.
+Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, accepted, 2023.
 [arxiv preprint](https://arxiv.org/abs/2211.12687)

### 2023-10-25 papers.qmd
add accepted envirometrics paper

@@
 
-D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)
-
 Christian A.
@@
 
+D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)
+
 **J.
@@
 Tucker** and D.
-Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, accepted, 2023.
-[arxiv preprint](https://arxiv.org/abs/2211.12687)
+Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, 10.1002/env.2826, 2023.
+[PDF](Papers/Envirometics23_ElasticChangeDetection.pdf)
 

### 2023-11-01 papers.qmd
add paper

@@
 ## 2023
+A.
+McCombs, M.
+A.
+Ausdemore, K.
+Goode, J.
+G.
+Huerta, K.
+Shuler, **J.
+D.
+Tucker**, A.
+Zhang, and D.
+Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*.
+submitted, 2023.
+
 J.
@@
 Huerta, and K.
-Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, submitted 2023.
+Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, in revision 2023.
 
 D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2308.05915)
+
+D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)
 
@@
 [PDF](Papers/SPIE23.pdf)
-
-D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)
 

### 2023-11-28 papers.qmd
minor update

@@
 Huerta, and K.
-Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, in revision 2023.
+Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, accepted 2023.
 

### 2023-12-11 papers.qmd
add slides

@@
 ## Invited Talks
+"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/ASA_23_Calibration/index.html)
+
 "Elasic Bayesian Model Calibration" *FSU Shape Group Statistical Meeting*, January 24, 2023, [Slides](https://jdtuck.github.io/presentations/FSU_Jan23/FSU_Jan23.html)

### 2023-12-15 papers.qmd
add paper
add JAP paper

@@
 ## 2023
+R. Darling, G. S. Clark, and **J. D. Tucker**, "Hidden Ancestor Graphs: Models for Detagging Property Graphs", *arXiv:2102.09581 [math.PR]*. 2023 [arxiv preprint](https://arxiv.org/abs/2102.09581)
+
 A.
@@
 Huerta, and K.
-Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, accepted 2023.
+Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, vol.
+134, no.
+23, 2023.
+[PDF](Papers/JAP23_calibration.pdf)
 

### 2024-02-09 papers.qmd
update for 2024
fix link

@@
 
-## 2023
-R. Darling, G. S. Clark, and **J. D. Tucker**, "Hidden Ancestor Graphs: Models for Detagging Property Graphs", *arXiv:2102.09581 [math.PR]*. 2023 [arxiv preprint](https://arxiv.org/abs/2102.09581)
-
+## 2024
 A.
@@
 
+D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2308.05915)
+
+D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)
+
+## 2023
+R. Darling, G. S. Clark, and **J. D. Tucker**, "Hidden Ancestor Graphs: Models for Detagging Property Graphs", *arXiv:2102.09581 [math.PR]*. 2023 [arxiv preprint](https://arxiv.org/abs/2102.09581)
+
 J.
@@
 [PDF](Papers/JAP23_calibration.pdf)
-
-D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2308.05915)
-
-D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)
 
@@
 ## Invited Talks
-"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/ASA_23_Calibration/index.html)
+"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/presentations/ASA_23_Calibration/index.html)
 

### 2024-02-23 papers.qmd
add slides for purdue

--- 2023-12-15 papers.qmd
@@
 ## Invited Talks
-"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/ASA_23_Calibration/index.html)
+"Bayesian Model Calibration: An Elastic Approach" *Purdue Statistical Colloquium*, February 23, 2024, [Slides](https://jdtuck.github.io/presentations/Purdue_Feb24/Purdue_Feb24.html)
+
+"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/presentations/ASA_23_Calibration/index.html)
 

### 2024-06-04 papers.qmd
updates to slides and papers

@@
 Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*.
-submitted, 2023.
+accepted, 2023.
 
@@
 
-D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)
+D.
+Francom, **J.
+D.
+Tucker**, J.
+G.
+Huerta, K.
+Shuler, and D.
+Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, submitted, 2023.
+[arxiv preprint](https://arxiv.org/abs/2305.08834)
 
@@
 
-"Elastic Functional Data Analysis", *Brigham Young University Statistics Colloquium*, December 4, 2019
+"Elastic Functional Data Analysis", *Brigham Young University Statistics Colloquium*, December 4, 2019 [Slides](https://jdtuck.github.io/presentations/FDA_Overview/FDA_Overview.html)
 

### 2024-09-12 papers.qmd
updated papers

@@
 ## 2024
+N.
+Winovich, Nick, L.
+Moynihan, O.
+Abdelrahman, R.
+West, S.
+Dauphin, **J.
+D.
+Tucker**, G.
+Huerta, K.
+Potter, R.
+Forrest, C.
+Phillips, and M.
+Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Transactions on Geoscience and Remote Sensing*, submitted, 2024.
+
+J.E.
+Borgert, J.
+Hannig$, **J.D.
+Tucker**, L.
+Arbeeva, A.
+N.
+Buck, Y.
+M.
+Golightly, S.
+P.
+Messier, A.
+E.
+Nelson, and J.S.
+Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024.
+
 A.
@@
 Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*.
-accepted, 2023.
+10.3389/fnuen.2024.1331349, 2024.
+[PDF](Papers/SUR24FNE.pdf)
 
-D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2308.05915)
+D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, in revision, 2024. [arxiv preprint](https://arxiv.org/abs/2308.05915)
 
@@
 Shuler, and D.
-Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, submitted, 2023.
+Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, in revision, 2024.
 [arxiv preprint](https://arxiv.org/abs/2305.08834)

### 2024-09-21 papers.qmd
add paper
update
paper update

@@
 A.
+Heiskala, **J.
+D.
+Tucker**, P.
+Choudhary, R.
+Nedelec, J.
+Ronkainen, O.
+Sarala, M.
+Järvelin, M.
+J.
+Sillanpääm, and Sylvain Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, in revision, 2024.
+
+A.
 McCombs, M.
@@
 Shuler, and D.
-Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, in revision, 2024.
+Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, in accepted, 2024.
 [arxiv preprint](https://arxiv.org/abs/2305.08834)

### 2024-10-22 papers.qmd
typo
add preprint link
bugfix
updated patent

@@
 Borgert, J.
-Hannig$, **J.D.
+Hannig, **J.D.
 Tucker**, L.
@@
 Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024.
+[arxiv preprint](https://arxiv.org/abs/2409.13938)
 
@@
 Shuler, and D.
-Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, in accepted, 2024.
+Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, accepted, 2024.
 [arxiv preprint](https://arxiv.org/abs/2305.08834)
@@
 ## Patents
-"Method and system for training an artifical neural network utilizing physics based knowledge" US Patent No. Applied
+"Density-Based clustering of multidimensional Data" US Patent No. Applied
+
+"Method and system for training an artificial neural network utilizing physics based knowledge" US Patent No. Applied
 

### 2024-11-19 papers.qmd
add Stony Brook talk

--- 2024-09-12 papers.qmd
@@
 ## 2024
-N.
-Winovich, Nick, L.
-Moynihan, O.
-Abdelrahman, R.
-West, S.
-Dauphin, **J.
-D.
-Tucker**, G.
-Huerta, K.
-Potter, R.
-Forrest, C.
-Phillips, and M.
-Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Transactions on Geoscience and Remote Sensing*, submitted, 2024.
-
-J.E.
-Borgert, J.
-Hannig$, **J.D.
-Tucker**, L.
-Arbeeva, A.
-N.
-Buck, Y.
-M.
-Golightly, S.
-P.
-Messier, A.
-E.
-Nelson, and J.S.
-Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024.
-
 A.
@@
 Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*.
-10.3389/fnuen.2024.1331349, 2024.
-[PDF](Papers/SUR24FNE.pdf)
+submitted, 2023.
 
-D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, in revision, 2024. [arxiv preprint](https://arxiv.org/abs/2308.05915)
+D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2308.05915)
 
-D.
-Francom, **J.
-D.
-Tucker**, J.
-G.
-Huerta, K.
-Shuler, and D.
-Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, in revision, 2024.
-[arxiv preprint](https://arxiv.org/abs/2305.08834)
+D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)
 
@@
 ## Invited Talks
+"Elastic Functional Data Analsyis: with Applications to Functional Changepoint" *Stony Brook SIAM Speaker*, November 19, 2024, [Slides](https://jdtuck.github.io/presentations/StoneyBrook_Nov_24/StoneyBrook_Nov_24.html)
+
 "Bayesian Model Calibration: An Elastic Approach" *Purdue Statistical Colloquium*, February 23, 2024, [Slides](https://jdtuck.github.io/presentations/Purdue_Feb24/Purdue_Feb24.html)
@@
 
-"Elastic Functional Data Analysis", *Brigham Young University Statistics Colloquium*, December 4, 2019 [Slides](https://jdtuck.github.io/presentations/FDA_Overview/FDA_Overview.html)
+"Elastic Functional Data Analysis", *Brigham Young University Statistics Colloquium*, December 4, 2019
 

### 2024-12-17 papers.qmd
update

--- 2024-10-22 papers.qmd
@@
 J.
-Sillanpääm, and Sylvain Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, in revision, 2024.
+Sillanpääm, and Sylvain Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, accepted, 2024.
 

### 2025-01-02 software.qmd
add software
update paper for veesa

@@
 [PDF](Papers/SPATSTAT18_STPP.pdf)
+
+## `veesa`
+I'm a devloper of the `veesa` R package ([GitHub](https://github.com/sandialabs/veesa)).
+
+A R package for VEESA Pipeline for Explainable Machine Learning with Functional Data frin oaoer K.
+Goode, J.
+D.
+Tucker, D.
+Ries, and H.
+Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Annals of Applied Statistics*, submitted, 2024.

### 2025-01-02 papers.qmd
added paper
update for 2025
fix spaces

@@
 
+## 2025
+
 ## 2024
+K. Goode, **J. D. Tucker**, D. Ries, and H. Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Annals of Applied Statistics*, submitted, 2024.
+
 N.
@@
 
-J.E.
+J.
+E.
 Borgert, J.
-Hannig, **J.D.
+Hannig, **J.
+D.
 Tucker**, L.
@@
 E.
-Nelson, and J.S.
+Nelson, and J.
+S.
 Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024.
@@
 J.
-Sillanpääm, and Sylvain Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, accepted, 2024.
+Sillanpääm, and S.
+Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, accepted, 2024.
 
@@
 [PDF](Papers/SUR24FNE.pdf)
-
-D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, in revision, 2024. [arxiv preprint](https://arxiv.org/abs/2308.05915)
 

### 2025-01-16 papers.qmd
fix paper
add arxiv

@@
 ## 2025
-
-## 2024
-K. Goode, **J. D. Tucker**, D. Ries, and H. Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Annals of Applied Statistics*, submitted, 2024.
+K.
+Goode, **J.
+D.
+Tucker**, D.
+Ries, and H.
+Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Computational Statistics and Data Analysis*, submitted, 2025.
+[arxiv preprint](https://arxiv.org/abs/2501.07602)
 
 N.
-Winovich, Nick, L.
+Winovich, L.
 Moynihan, O.
@@
 Phillips, and M.
-Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Transactions on Geoscience and Remote Sensing*, submitted, 2024.
+Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Transactions on Geoscience and Remote Sensing*, in revision, 2024.
 
+## 2024
 J.

### 2025-01-17 papers.qmd
add published paper

@@
 Sillanpääm, and S.
-Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, accepted, 2024.
+Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, 10.1038/s41366-025-01714-8, 2024.
+[PDF](Papers/Heiskala_et_al-2025-International_Journal_of_Obesity.pdf)
 

### 2025-01-22 software.qmd
add cran link

--- 2023-08-16 software.qmd
@@
 [PDF](Papers/SPATSTAT18_STPP.pdf)
+
+## `veesa`
+I'm a devloper of the `veesa` R package ([CRAN](https://cran.r-project.org/web/packages/veesa/index.html);[GitHub](https://github.com/sandialabs/veesa)).
+
+A R package for VEESA Pipeline for Explainable Machine Learning with Functional Data frin oaoer K.
+Goode, J.
+D.
+Tucker, D.
+Ries, and H.
+Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Annals of Applied Statistics*, submitted, 2025.

### 2025-02-19 papers.qmd
add publication details

@@
 Shuler, and D.
-Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, accepted, 2024.
-[arxiv preprint](https://arxiv.org/abs/2305.08834)
+Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, vol.
+13, no.
+1, 2025.
+[PDF](Papers/Francom-2025-Calibration-JUQ.pdf)
 

### 2025-04-24 software.qmd
update software

@@
 Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Annals of Applied Statistics*, submitted, 2025.
+
+## `impala`
+I'm a devloper of the `impala` R package ([GitHub](https://github.com/sandialabs/rImpala)).
+
+R library for modular Bayesian model calibration.
+Posterior exploration includes tempering and adaptive MCMC.
+This is an R tranlastion of the python library [impala](https://github.com/lanl/impala) by LANL

### 2025-04-28 papers.qmd
add patent number
add conformal paper
forgot title
add slides

@@
 ## 2025
+J.
+Adams, B.
+Berman, J.
+Michalenko, **J.
+D.
+Tucker**, "Conformal Anomaly Detection for Functional Data with Elastic Distance Metrics", *arXiv:2504.01172*, submitted, 2025.
+[arxiv preprint](https://arxiv.org/abs/2504.01172)
+
 K.
@@
 ## Invited Talks
+"Bayesian Model Calibration: An Elastic Appraoch" *Colorado State Univeristy Statistics Seminar*, April 28, 2025, [Slides](https://jdtuck.github.io/presentations/CSU_April25/CSU_April25.html)
+
 "Elastic Functional Data Analsyis: with Applications to Functional Changepoint" *Stony Brook SIAM Speaker*, November 19, 2024, [Slides](https://jdtuck.github.io/presentations/StoneyBrook_Nov_24/StoneyBrook_Nov_24.html)
@@
 
-"Method and system for training an artificial neural network utilizing physics based knowledge" US Patent No. Applied
+"Method and system for training an artificial neural network utilizing physics based knowledge" US Patent No. US12229934 [PDF](Papers/US12229934.pdf)
 

### 2025-04-28 papers.qmd
bugfix

@@
 ## Invited Talks
-"Bayesian Model Calibration: An Elastic Appraoch" *Colorado State Univeristy Statistics Seminar*, April 28, 2025, [Slides](https://jdtuck.github.io/presentations/CSU_April25/CSU_April25.html)
+"Bayesian Model Calibration: An Elastic Approach" *Colorado State Univeristy Statistics Seminar*, April 28, 2025, [Slides](https://jdtuck.github.io/presentations/CSU_April25/CSU_April25.html)
 

### 2025-04-28 papers.qmd
bugfix

@@
 ## Invited Talks
-"Bayesian Model Calibration: An Elastic Approach" *Colorado State Univeristy Statistics Seminar*, April 28, 2025, [Slides](https://jdtuck.github.io/presentations/CSU_April25/CSU_April25.html)
+"Bayesian Model Calibration: An Elastic Approach" *Colorado State University Statistics Seminar*, April 28, 2025, [Slides](https://jdtuck.github.io/presentations/CSU_April25/CSU_April25.html)
 

### 2025-09-12 software.qmd
update software section

@@
 This is an R tranlastion of the python library [impala](https://github.com/lanl/impala) by LANL
+
+## `mvBayes`
+I'm a developer of the `mvBayes` R and and Python Package ([Github - R](https://github.com/sandialabs/mvBayesR);[Github - Python](https://github.com/sandialabs/mvBayesPy))
+
+Implementation of the multivariate Bayesian regression (mvBayes) framework.
+Decomposes a multivariate/functional response using a user-specified orthogonal basis decomposition, and then models each basis component independently using an arbitrary user-specified (univariate) Bayesian regression model.
+Includes prediction and plotting methods.

### 2025-10-03 papers.qmd
add paper award
updates

@@
 ## 2025
-J.
-Adams, B.
-Berman, J.
-Michalenko, **J.
-D.
-Tucker**, "Conformal Anomaly Detection for Functional Data with Elastic Distance Metrics", *arXiv:2504.01172*, submitted, 2025.
-[arxiv preprint](https://arxiv.org/abs/2504.01172)
-
 K.
@@
 Ries, and H.
-Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Computational Statistics and Data Analysis*, submitted, 2025.
+Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Journal of Data Science*, in revision, 2025.
 [arxiv preprint](https://arxiv.org/abs/2501.07602)
@@
 Phillips, and M.
-Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Transactions on Geoscience and Remote Sensing*, in revision, 2024.
+Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing*, submitted, 2024.
 
-## 2024
+J.
+Adams, B.
+Berman, J.
+Michalenko, **J.
+D.
+Tucker**, "Conformal Anomaly Detection for Functional Data with Elastic Distance Metrics", *arXiv:2504.01172*, 2025.
+[arxiv preprint](https://arxiv.org/abs/2504.01172)
+
 J.
@@
 S.
-Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024.
+Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, accepted, 2025.
 [arxiv preprint](https://arxiv.org/abs/2409.13938)
 
+## 2024
 A.
@@
 Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, 10.1002/env.2826, 2023.
-[PDF](Papers/Envirometics23_ElasticChangeDetection.pdf)
+[PDF](Papers/Envirometics23_ElasticChangeDetection.pdf) **2024 Wiley-TIES Best Environmetrics Paper Award**
 

### 2025-10-24 papers.qmd
add JASA paper
add TIES talk

@@
 S.
-Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, accepted, 2025.
-[arxiv preprint](https://arxiv.org/abs/2409.13938)
+Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, 10.1080/01621459.2025.2572778, 2025.
+[PDF](Papers/JASA25_Borgert.pdf)
 
@@
 ## Invited Talks
+"Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources" *Environmentrics TIES Webinar*, October 24, 2025, [Slides](https://jdtuck.github.io/presentations/TIES_Webinar_Oct_25/TIES_Webinar_Oct25.html) [Video](https://www.youtube.com/@environmetricswebinar3128)
+
 "Bayesian Model Calibration: An Elastic Approach" *Colorado State University Statistics Seminar*, April 28, 2025, [Slides](https://jdtuck.github.io/presentations/CSU_April25/CSU_April25.html)
@@
 
-"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/presentations/ASA_23_Calibration/index.html)
+"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/presentations/ASA_23_Calibration/index.html) [Video](https://www.youtube.com/watch?v=UNyOfL_zLX8&t=1469s)
 

### 2025-11-28 software.qmd
add packages

@@
 Includes prediction and plotting methods.
+
+## `BASS`
+I'm a developer of the `BASS` MATLAB Package ([Github](https://github.com/sandialabs/bass_matlab))
+
+Implementation of Bayesian Adaptive Spline Surfaces in MATLAB. This is a MATLAB translation of the python library [pyBASS](https://github.com/lanl/pyBASS)
+
+## `BayesPPR`
+I'm a developer of the `BayesPPR` MATLAB Package ([Github](https://github.com/sandialabs/bayesppr_matlab))
+
+A MATLAB implementation of Bayesian Projection Pursuit Regression (BayesPPR). This is a MATLAB translation of the python library [pyBayesPPR](https://github.com/gqcollins/pyBayesPPR)
